Incentivizing Exploration by Heterogeneous Users

### 2018-02-16 algorithm.tex
edited payment proof to use new lemmas

To formally reason about the event that the estimates of arms'
attributes vectors are accurate enough --- or fail to be so ---
we define the events
$\AccE{t}{i}{j}{\epsilon} := [|\ArmE{t}{i}{j} - \Arm{i}{j}| \leq \epsilon]$
that attribute $j$ of arm $i$ at time $t$ is estimated to
within accuracy $\epsilon$ or better.
Then, 
$\AccEU{t}{\epsilon} = \bigcap_{i,j} \AccE{t}{i}{j}{\epsilon}$
is the event that at time $t$, all arm attribute
estimates are accurate to within $\epsilon$ simultaneously.
We will then show that for suitable choices of $t, x$,
the events \AccE{t}{i}{j}{x}
(and hence, by union bound, \AccEU{t}{\epsilon})
have high probability,
and that when they do, myopic agents do not make large mistakes.

@@

\begin{lemma} \label{lem:round-prob}
Recall that $\sigma$ is the standard deviation of the Gaussian noise.
Let \LatePhase be a phase cutoff, 
and let $\epsilon_n, \epsilon'_n > 0$ be functions satisfying that
$\sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1) + \frac{n \epsilon_n^2}{16 \sigma^2}}
\leq \frac{n \epsilon'_n}{2 \sigma}$,
for all $n \geq \LatePhase$.
Let $\tau_s$ be a stopping time
(which may depend on the entire past history)
which is almost surely in phase $s$,
i.e., satisfying $\tau \in [t_s, t_{s+1})$ almost surely.

Then, for any arm $i$, attribute $j$, and phase $s \geq \LatePhase$,
we have that
$\Prob{\AccE{\tau_s}{i}{j}{\epsilon'_s}}
\geq 1 - 24 \exp\left(-\frac{1.8 s \epsilon_s^2}{16 \sigma^2} \right)$.
\end{lemma}

@@

\begin{extraproof}{Lemma~\ref{lem:round-prob}}
Fix an arm $i$ and attribute $j$.
By the assumptions of the lemma,
the stopping time $\tau_s$ is such that almost surely,
each arm --- and in particular arm $i$ --- has been pulled at least
$s \geq \LatePhase$ times at time $\tau_s$.
Define $J$ to be the number of times that $i$ has been pulled at
time $\tau_s$.
For any $n \geq 1$, let $k_n$ be the time step right after arm $i$ has
been pulled for the \Kth{n} time. Define
$S_n := \frac{n \cdot (\ArmE{k_n}{i}{j} - \Arm{i}{j})}{2 \sigma}$
to be the sum of all attribute-$j$ noise components up to and
including the \Kth{n} pull of arm $i$,
renormalized to have standard deviation $1/2$.
The $S_n$ define an unbiased half-subgaussian random walk,
and we can therefore apply Lemma~\ref{lem:ACI-inequality} to them and
the stopping time $J$.
Specifically, we set $b = \frac{\epsilon_J^2}{16 \sigma^2}$,
and obtain that

\begin{align*}
\Prob{J < \infty \mbox{ and } S_J \geq 
\sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1) + \frac{J \epsilon_J^2}{16 \sigma^2}}}
& \leq 12 \exp \left( \frac{-1.8 J \epsilon_J^2}{16 \sigma^2} \right).
\end{align*}

@@

\begin{align*}
\Prob{J < \infty \mbox{ and } |S_J| \geq 
\sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1) + \frac{J \epsilon_J^2}{16 \sigma^2}}}
& \leq 24 \exp \left( \frac{-1.8 J \epsilon_J^2}{16 \sigma^2} \right).
\end{align*}

Because $J$ will be finite with probability 1, we can drop the
$J < \infty$ part of the event:
\begin{align*}
& \Prob{S_J \geq 
\sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1) + \frac{J^2 \epsilon_J^2}{16
    \sigma^2}}}\\
= & \Prob{J < \infty \mbox{ and } S_J \geq 
\sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1) + \frac{J^2 \epsilon_J^2}{16
    \sigma^2}}}.
\end{align*}

In the high-probability case, we now apply the assumed inequality
between $\epsilon_J$ and $\epsilon'_J$, to obtain that
\[
|S_J| \; \leq \;
\sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1) + \frac{J \epsilon_J^2}{16 \sigma^2}}
\; \leq \; \frac{J \epsilon'_J}{2 \sigma}.
\]

Substituting the definition of $S_J$ and canceling common terms,
the inequality implies that
$|\ArmE{k_J}{i}{j} - \Arm{i}{j}| \leq \epsilon'_J$.
The choice of $J$ ensures that
$\ArmE{k_J}{i}{j} = \ArmE{\tau_s}{i}{j}$,
and we have thus shown that
$|\ArmE{\tau_s}{i}{j} - \Arm{i}{j}| \leq \epsilon'_s$.
\end{extraproof}

Next, we show the complementary part:
when \AccE{t}{\epsilon} happens, no myopic agent incurs large regret.

\begin{lemma} \label{lem:right-choice}
Let $\epsilon > 0$ be arbitrary.
When \AccEU{t}{\epsilon} happens,
no agent \AgV will pull a highly suboptimal arm, i.e., an arm $i$ with 
$\AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{i}) > 2\Diam d \epsilon$.
\end{lemma}

\begin{proof}
By definition, when \AccEU{t}{\epsilon} happens,
for all arms $i$ and attributes $j$,
all arm attribute estimates are accurate to within $\epsilon$,
in the sense that
$|\ArmE{\tau}{i}{j} - \Arm{i}{j}| \leq \epsilon$.

Consider any agent type \AgV.
Let $i \neq \Best{\AgV}$ be any arm
with much smaller true reward than the best arm:
$\AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{i}) > 2\Diam d \epsilon$.
Because each coordinate of \ArmEV{t}{\Best{\AgV}} and of
\ArmEV{t}{i} is estimated accurately to within $\epsilon$, 
we get that 
$\AgV \cdot (\ArmEV{t}{\Best{\AgV}} - \ArmV{\Best{\AgV}})
\geq - \Diam d \epsilon$
and
$\AgV \cdot (\ArmEV{t}{i} - \ArmV{i}) \leq \Diam d \epsilon$.
Hence,

\begin{align}
\AgV \cdot (\ArmEV{t}{\Best{\AgV}} - \ArmEV{t}{i})
& =
\AgV \cdot (\ArmEV{t}{\Best{\AgV}} - \ArmV{\Best{\AgV}})
+ \AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{i})
+ \AgV \cdot (\ArmV{i} - \ArmEV{t}{i}) \nonumber\\
& > -\Diam d \epsilon + 2 \Diam d \epsilon - \Diam d \epsilon
\; = \; 0, \label{equ:choice}
\end{align}
which means that the agent with type \AgV will not pull arm $i$.
\end{proof}

@@

As a first step towards bound the total payment (and also regret),
we show that for sufficiently late phases,
under the event \AccEU{t}{\epsilon} for suitably small $\epsilon$,
the algorithm does not offer any payments.

@@

To make this intuition precise, we set
$\delta = \frac{\MinProb}{2 \TieDensity}$,
and $\epsilon = \epsilon' = \frac{\delta}{2 \Diam d}$
(which is independent of the phase number $s$).
The cutoff point between early and late phases is now set to
$\EvenLaterPhase = \max(2, \frac{30 \sigma^3}{\epsilon^3}, \exp(\frac{2}{\MinProb}))$.
We will verify below that
$\sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1) + \frac{n \epsilon^2}{16 \sigma^2}}
\leq \frac{n \epsilon}{2 \sigma}$
for all $n \geq \max(2, \frac{30 \sigma^3}{\epsilon^3})$.

@@

By Lemma~\ref{lem:round-prob} (with our choice of $\epsilon = \epsilon'$),
and a union bound over all $i,j$, we bound the probability
$\Prob{\AccEU{\tau_s}{\epsilon}}
\geq 1 - 24 \ARMNUM d \cdot \exp\left(-\frac{1.8 s \epsilon^2}{16 \sigma^2} \right)$.
And by Lemma~\ref{lem:no-incentives},
under the event ${\mathcal E}_{\tau_s}(\epsilon)$,
arm $i$ is not payment-eligible.

@@

It remains to show that
$\sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1) + \frac{n \epsilon^2}{16 \sigma^2}}
\leq \frac{n \epsilon}{2 \sigma}$
for all $n \geq \max(2, \frac{30 \sigma^3}{\epsilon^3}$.
We first use that $\sqrt{\cdot}$ is sublinear to bound
\[
  \sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1) + \frac{n \epsilon^2}{16 \sigma^2}}
\; \leq \; \sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1)} + \frac{n \epsilon}{4 \sigma}
\]
(here we use the fact $\sqrt{n} \leq n$).
Next, we show that
$\sqrt{0.6 n \log (\log_{1.1}(n) + 1)} \leq \frac{n \epsilon}{4 \sigma}$;
then, adding the two terms gives the desired bound.

By squaring the claimed statement and rearranging,
it is equivalent to show that
$\frac{n}{\log(\log_{1.1}(n)+1)} \geq \frac{9.6\sigma^2}{\epsilon^2}$.
Because $n \geq 2$,
a numerical calculation and derivative test shows that
$\frac{n}{\log(\log_{1.1}(n)+1)} \geq n^{2/3}$,
and because $n \geq \frac{30 \sigma^3}{\epsilon^3}$,
we get that
$n^{2/3} \geq \frac{9.6 \sigma^2}{\epsilon^2}$, completing the proof.

@@

To bound the probability of \AccEU{\tau_s^k}{\frac{g(s)}{2\Diam d}},
we use Lemma~\ref{lem:round-prob}
(with $\epsilon_s = \epsilon'_s = \frac{g(s)}{2 \Diam d}$
and a stopping time of $\tau_s^k$).
We first verify that this choice of $\epsilon_s, \epsilon'_s$
satisfies the assumption of Lemma~\ref{lem:round-prob} for all
$s \geq 2$,
i.e., that
$\sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1) + \frac{n \epsilon_n^2}{16 \sigma^2}}
\leq \frac{n \epsilon_n}{2 \sigma}$
for all $n \geq 2$.
Substituting that
$\epsilon_n = \frac{g(n)}{2 \Diam d} = \sqrt{\frac{32\log(T) \cdot \sigma^2}{1.8 n}}$,
the left-hand side is

@@

Now, by Lemma~\ref{lem:round-prob} and a union bound over all arms $i$
and attributes $j$, we get that 
\begin{align*}
\Prob{\AccEU{\tau_s^k}{\epsilon_s}}
& \leq 24 \ARMNUM d \cdot \exp \left( \frac{-1.8 s x^2}{16 \sigma^2} \right)
\; = \; \frac{24 \ARMNUM d}{T^2}.
\end{align*}

>>>>

To formally reason about the event that the estimates of arms'
attributes vectors are accurate enough --- or fail to be so ---
we define the events
$\AccE{t}{i}{j}{x} := [|\ArmE{t}{i}{j} - \Arm{i}{j}| \leq x]$
that attribute $j$ of arm $i$ at time $t$ is estimated to
within accuracy $x$ or better.
Then, 
$\AccEU{t}{x} = \bigcap_{i,j} \AccE{t}{i}{j}{x}$
is the event that at time $t$, all arm attribute
estimates are accurate to within $x$ simultaneously.
We will then show that for suitable choices of $t, x$,
the events \AccE{t}{i}{j}{x}
(and hence, by union bound, \AccEU{t}{x})
have high probability,
and that when they do, myopic agents do not make large mistakes.

@@

\begin{lemma} \label{lem:round-prob}
Recall that $\sigma$ is the standard deviation of the Gaussian noise.
Let \LatePhase be a phase cutoff, 
and let $x_n, x'_n > 0$ be functions satisfying that
$\sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1) + \frac{n x_n^2}{16 \sigma^2}}
\leq \frac{n x'_n}{2 \sigma}$,
for all $n \geq \LatePhase$.
Let $\tau_s$ be a stopping time
(which may depend on the entire past history)
which is almost surely in phase $s$,
i.e., satisfying $\tau \in [t_s, t_{s+1})$ almost surely.

Then, for any arm $i$, attribute $j$, and phase $s \geq \LatePhase$,
we have that
$\Prob{\AccE{\tau_s}{i}{j}{x'_s}}
\geq 1 - 24 \exp\left(-\frac{1.8 s x_s^2}{16 \sigma^2} \right)$.
\end{lemma}

@@

\begin{extraproof}{Lemma~\ref{lem:round-prob}}
Fix an arm $i$ and attribute $j$.
By the assumptions of the lemma,
the stopping time $\tau_s$ is such that almost surely,
each arm --- and in particular arm $i$ --- has been pulled at least
$s \geq \LatePhase$ times at time $\tau_s$.
Define $J$ to be the number of times that $i$ has been pulled at
time $\tau_s$.
For any $n \geq 1$, let $k_n$ be the time step right after arm $i$ has
been pulled for the \Kth{n} time. Define
$S_n := \frac{n \cdot (\ArmE{k_n}{i}{j} - \Arm{i}{j})}{2 \sigma}$
to be the sum of all attribute-$j$ noise components up to and
including the \Kth{n} pull of arm $i$,
renormalized to have standard deviation $1/2$.
The $S_n$ define an unbiased half-subgaussian random walk,
and we can therefore apply Lemma~\ref{lem:ACI-inequality} to them and
the stopping time $J$.
Specifically, we set $b = \frac{x_J^2}{16 \sigma^2}$,
and obtain that

\begin{align*}
\Prob{J < \infty \mbox{ and } S_J \geq 
\sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1) + \frac{J x_J^2}{16 \sigma^2}}}
& \leq 12 \exp \left( \frac{-1.8 J x_J^2}{16 \sigma^2} \right).
\end{align*}

@@

\begin{align*}
\Prob{J < \infty \mbox{ and } |S_J| \geq 
\sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1) + \frac{J x_J^2}{16 \sigma^2}}}
& \leq 24 \exp \left( \frac{-1.8 J x_J^2}{16 \sigma^2} \right).
\end{align*}

Because $J$ will be finite with probability 1, we can drop the
$J < \infty$ part of the event:
\begin{align*}
& \Prob{S_J \geq 
\sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1) + \frac{J^2 x_J^2}{16
    \sigma^2}}}\\
= & \Prob{J < \infty \mbox{ and } S_J \geq 
\sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1) + \frac{J^2 x_J^2}{16
    \sigma^2}}}.
\end{align*}

In the high-probability case, we now apply the assumed inequality
between $x_J$ and $x'_J$, to obtain that
\[
|S_J| \; \leq \;
\sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1) + \frac{J x_J^2}{16 \sigma^2}}
\; \leq \; \frac{J x'_J}{2 \sigma}.
\]

Substituting the definition of $S_J$ and canceling common terms,
the inequality implies that
$|\ArmE{k_J}{i}{j} - \Arm{i}{j}| \leq x'_J$.
The choice of $J$ ensures that
$\ArmE{k_J}{i}{j} = \ArmE{\tau_s}{i}{j}$,
and we have thus shown that
$|\ArmE{\tau_s}{i}{j} - \Arm{i}{j}| \leq x'_s$.
\end{extraproof}

Next, we show the complementary part:
when \AccE{t}{x} happens, no myopic agent incurs large regret.

\begin{lemma} \label{lem:right-choice}
Let $x > 0$ be arbitrary.
When \AccEU{t}{x} happens,
no agent \AgV will pull a highly suboptimal arm, i.e., an arm $i$ with 
$\AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{i}) > 2\Diam d x$.
\end{lemma}

\begin{proof}
By definition, when \AccEU{t}{x} happens,
for all arms $i$ and attributes $j$,
all arm attribute estimates are accurate to within $x$,
in the sense that
$|\ArmE{\tau}{i}{j} - \Arm{i}{j}| \leq x$.

Consider any agent type \AgV.
Let $i \neq \Best{\AgV}$ be any arm
with much smaller true reward than the best arm:
$\AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{i}) > 2\Diam d x$.
Because each coordinate of \ArmEV{t}{\Best{\AgV}} and of
\ArmEV{t}{i} is estimated accurately to within $x$, 
we get that 
$\AgV \cdot (\ArmEV{t}{\Best{\AgV}} - \ArmV{\Best{\AgV}})
\geq - \Diam d x$
and
$\AgV \cdot (\ArmEV{t}{i} - \ArmV{i}) \leq \Diam d x$.
Hence,

\begin{align}
\AgV \cdot (\ArmEV{t}{\Best{\AgV}} - \ArmEV{t}{i})
& =
\AgV \cdot (\ArmEV{t}{\Best{\AgV}} - \ArmV{\Best{\AgV}})
+ \AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{i})
+ \AgV \cdot (\ArmV{i} - \ArmEV{t}{i}) \nonumber\\
& > -\Diam d x + 2 \Diam d x - \Diam d x
\; = \; 0, \label{equ:choice}
\end{align}
which means that the agent with type \AgV will not pull arm $i$.
\end{proof}

@@

As a first step towards bound the total payment (and also regret),
we show that for sufficiently late phases,
under the event \AccEU{t}{x} for suitably small $x$,
the algorithm does not offer any payments.

@@

To make this intuition precise, we set
$\delta = \frac{\MinProb}{2 \TieDensity}$,
and $x = x' = \frac{\delta}{2 \Diam d}$
(which is independent of the phase number $s$).
The cutoff point between early and late phases is now set to
$\EvenLaterPhase = \max(2, \frac{30 \sigma^3}{x^3}, \exp(\frac{2}{\MinProb}))$.
We will verify below that
$\sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1) + \frac{n x^2}{16 \sigma^2}}
\leq \frac{n x}{2 \sigma}$
for all $n \geq \max(2, \frac{30 \sigma^3}{x^3})$.

@@

By Lemma~\ref{lem:round-prob} (with our choice of $x = x'$),
and a union bound over all $i,j$, we bound the probability
$\Prob{\AccEU{\tau_s}{x}}
\geq 1 - 24 \ARMNUM d \cdot \exp\left(-\frac{1.8 s x^2}{16 \sigma^2} \right)$.
And by Lemma~\ref{lem:no-incentives},
under the event ${\mathcal E}_{\tau_s}(x)$,
arm $i$ is not payment-eligible.

@@

It remains to show that
$\sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1) + \frac{n x^2}{16 \sigma^2}}
\leq \frac{n x}{2 \sigma}$
for all $n \geq \max(2, \frac{30 \sigma^3}{x^3}$.
We first use that $\sqrt{\cdot}$ is sublinear to bound
\[
  \sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1) + \frac{n x^2}{16 \sigma^2}}
\; \leq \; \sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1)} + \frac{n x}{4 \sigma}
\]
(here we use the fact $\sqrt{n} \leq n$).
Next, we show that
$\sqrt{0.6 n \log (\log_{1.1}(n) + 1)} \leq \frac{n x}{4 \sigma}$;
then, adding the two terms gives the desired bound.

By squaring the claimed statement and rearranging,
it is equivalent to show that
$\frac{n}{\log(\log_{1.1}(n)+1)} \geq \frac{9.6\sigma^2}{x^2}$.
Because $n \geq 2$,
a numerical calculation and derivative test shows that
$\frac{n}{\log(\log_{1.1}(n)+1)} \geq n^{2/3}$,
and because $n \geq \frac{30 \sigma^3}{x^3}$,
we get that
$n^{2/3} \geq \frac{9.6 \sigma^2}{x^2}$, completing the proof.

@@

To bound the probability of \AccEU{\tau_s^k}{\frac{g(s)}{2\Diam d}},
we use Lemma~\ref{lem:round-prob}
(with $x_s = x'_s = \frac{g(s)}{2 \Diam d}$
and a stopping time of $\tau_s^k$).
We first verify that this choice of $x_s, x'_s$
satisfies the assumption of Lemma~\ref{lem:round-prob} for all
$s \geq 2$,
i.e., that
$\sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1) + \frac{n x_n^2}{16 \sigma^2}}
\leq \frac{n x_n}{2 \sigma}$
for all $n \geq 2$.
Substituting that
$x_n = \frac{g(n)}{2 \Diam d} = \sqrt{\frac{32\log(T) \cdot \sigma^2}{1.8 n}}$,
the left-hand side is

@@

Now, by Lemma~\ref{lem:round-prob} and a union bound over all arms $i$
and attributes $j$, we get that 
\begin{align*}
\Prob{\AccEU{\tau_s^k}{x_s}}
& \leq 24 \ARMNUM d \cdot \exp \left( \frac{-1.8 s x^2}{16 \sigma^2} \right)
\; = \; \frac{24 \ARMNUM d}{T^2}.
\end{align*}

### 2018-02-16 payment-proof.tex
edited payment proof to use new lemmas

\begin{proof}
The proof idea is quite similar to the proof of
Lemma~\ref{lem:round-prob};
however, the specific form of the envelopes necessitates some subtle
changes in the specific forms of the bounds used.
For \SP to be in \Env{\ell}, by definition,
for at least one time $t$,
at least one coordinate of at least one arm's estimation error must
exceed $g(s(t,\SP),\ell-1)$.
For now, fix an arm $i$ and coordinate $j$.

Recall that $\NumPull{t}{i}(\SP) \geq s(t,\SP)$ is the number of times
that arm $i$ has been pulled by time $t$ under \SP.
We define the scaled estimation error
$S_{i,j}(t) := \frac{\NumPull{t}{i} \cdot \Err{t}{i}{j}}{2\sigma}$.
The advantage of $S_{i,j}(t)$ is that it is 
a summation of $1/2$-Gaussian random variables, 
so we will be able to apply Lemma~\ref{lem:ACI-inequality}.
First notice that we can express the desired probability as follows:

\begin{align*}
\Prob{|\Err{t}{i}{j}| \geq g(s(t,\SP), \ell-1)}
& = \Prob{S_{i,j}(t) \geq \frac{6\NumPull{t}{i}(\ell-1)}{s(t,\SP)^{2/5}}}\\
& \leq \; \Prob{S_{i,j}(t) \geq 6\NumPull{t}{i}^{3/5}(\ell-1)}. 
\end{align*}

We will show below that
$5 n^{3/5} \geq \sqrt{0.6n \log(\log_{1.1}(n)+1)}$
for all $n \geq 1$.
Applying this inequality and sublinearity of $\sqrt{\cdot}$,
we obtain that

\begin{align*}
6 \NumPull{t}{i}^{3/5}(\ell-1)
& \geq 5 \NumPull{t}{i}^{3/5} + \NumPull{t}{i}^{3/5}(\ell-1)  \\
& \geq \sqrt{0.6 \NumPull{t}{i} \log(\log_{1.1}(\NumPull{t}{i})+1)}
     + \sqrt{(\ell-1)^2 \NumPull{t}{i}}  \\
& \geq \sqrt{0.6\NumPull{t}{i}\log(\log_{1.1}(\NumPull{t}{i})+1)+(\ell-1)^2 \NumPull{t}{i}}
\; =: \; h(\NumPull{t}{i}).
\end{align*}

Let the random stopping time $\tau_{i,j}$ be the first value of
\NumPull{t}{i} (i.e., the first pull of arm $i$) such that 
$S_{i,j}(\tau_{i,j}) > h(\NumPull{t}{i})$.
$\tau_{i,j} = \infty$ means that the estimation error never exceeds 
$h(\NumPull{t}{i})$.
We apply Lemma~\ref{lem:ACI-inequality}
to $S_{i,j}(t)$, with a stopping time of $\tau_{i,j}$ and
with $b = (\ell-1)^2$.
We obtain that the probability that $\tau_{i,j} < \infty$ and 
$S_{i,j}(\tau_{i,j}) > h(\tau_{i,j})$ is at most
$12 \e^{-1.8 b}$.
By definition of $\tau_{i,j}$, the event is the same as simply
$\tau_{i,j} < \infty$.
Applying the lemma again to $-S_{i,j}(\tau_{i,j})$,
and taking a union bound over both cases,
gives us that the probability that there is \emph{any} time $t$ with
$|S_{i,j}(\NumPull{t}{i})| > h (\NumPull{t}{i})$
is at most $24 \e^{-1.8 b(n)}$.
Hence, the probability that the error at \emph{any} time $t$ exceeds
$g(s(t,\SP), \ell-1)$ is bounded by 
\begin{align*}
\Prob{|\Err{t}{i}{j}| \geq g(s(t,\SP), \ell-1)}
& \leq 24 \e^{-1.8(\ell-1)^2}.
\end{align*}
Now, taking a union bound over all arms $i$ and
coordinates $j$ completes the proof.

It remains to show that
$5 n^{3/5} \geq \sqrt{0.6n \log(\log_{1.1}(n)+1)}$
for all $n \geq 1$.
By squaring the inequality and canceling out a factor $n$,
the statement is equivalent to showing that
$25 n^{1/5} \geq \log(\log_{1.1}(n)+1)$.
We will show the stronger statement that
$25 n^{1/5} \geq \log_{1.1}(n)+1$.  
To see this, notice that the derivative of the left-hand side is
always strictly larger than the derivative of the right-hand side,
so the difference between the sides is minimized at $n=1$,
where it is positive. 
\end{proof}

@@

\begin{proof}
The proof is similar to that of Lemma~\ref{lem:numP}.
Fix a sample path $\SP \in \Env{\ell}$.
Consider a phase $s > h(\ell)$.

By definition of \Env{\ell}, the coordinate-wise estimation errors at
times $t$ in phase $s$ are
$|\Arm{i}{j} - \ArmE{t}{i}{j}| \leq g(s,\ell)$.
In particular, all agent typs \AgV whose preference for their best arm
is sufficiently clear
($\AgV \cdot \ArmV{\Best{\AgV}} - \AgV \cdot \ArmV{\Second{\AgV}}
> 2\Diam d g(s,\ell)$) will pull their best arm.

By Lemma~\ref{lem:sdelta}, the \emph{total} measure of agents (across
all arms) whose best and second-best arm differ in utility by at most
$2\Diam d \cdot g(s,\ell)$ is at most $2L \Diam d \cdot g(s,\ell)$.
Substituting the definition of $g$, because 
$s > h(\ell) \geq \left( \frac{48 \sigma \ell \TieDensity \Diam d}{\MinProb} \right)^{5/2}$,
the total measure of these agents is bounded by $\MinProb/2$.

By Assumption~\ref{A3}, at least a \MinProb fraction of agents have
$i$ as their best arm, so even with estimation errors, at least
$\MinProb - \MinProb/2 = \MinProb/2$ fraction will still prefer to
pull arm $i$.

Because $s > h(\ell) \geq \exp(\frac{2}{\MinProb})$, 
we get that $1/\log(s) \leq \MinProb/2$, so in phase $s$,
the algorithm will not incentivize any arms whose pulling probability
is more than $\MinProb/2$, which is all arms.
So no payments will be made in phase $s$.
\end{proof}

>>>>

\begin{proof}
For \SP to be in \Env{\ell}, by definition,
for at least one time $t$,
at least one coordinate of at least one arm's estimation error must
exceed $g(s(t,\SP),\ell-1)$.
For now, fix an arm $i$ and coordinate $j$.

Define $x_s := \frac{4 \sigma (\ell-1)}{s^{1/2}}$ and
$x'_s := g(s, \ell-1) = \frac{12 \sigma (\ell-1)}{s^{2/5}}$.

Recall that $\NumPull{t}{i}(\SP) \geq s(t,\SP)$ is the number of times
that arm $i$ has been pulled by time $t$ under \SP.
Let the random stopping time $\tau_{i,j}$ be the first value of
\NumPull{t}{i} (i.e., the first pull of arm $i$) such that 
the estimation error of attribute $j$ of arm $i$ exceeds
$g(\NumPull{t}{i}, \ell-1)$.
$\tau_{i,j} = \infty$ means that the estimation error never exceeds 
$g(\NumPull{t}{i}, \ell-1)$.
We next verify that $x_s, x'_s$ as we defined them satisfy the 
assumption 
\[
  \sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1) + \frac{n x_n^2}{16 \sigma^2}}
  \; \leq \; \frac{n x'_n}{2 \sigma}
\]
of Lemma~\ref{lem:round-prob}, for all $n \geq 1$.
First, we show that
$\sqrt{0.6n \log(\log_{1.1}(n)+1)} \leq 5 n^{3/5}$
for all $n \geq 1$.
By squaring the inequality and canceling out a factor $n$,
the statement is equivalent to showing that
$25 n^{1/5} \geq \log(\log_{1.1}(n)+1)$.
Indeed, a stronger statement holds, namely, that
$25 n^{1/5} \geq \log_{1.1}(n)+1$.  
To see this, notice that the derivative of the left-hand side is
always strictly larger than the derivative of the right-hand side,
so the difference between the sides is minimized at $n=1$,
where it is positive. 
Using this inequality and subadditivity of $\sqrt{\cdot}$, we can bound

\[
  \sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1) + \frac{n x_n^2}{16 \sigma^2}}
\; \leq \;
  5 n^{3/5} + \frac{\sqrt{n} x_n}{4 \sigma}
\; = \; 
  5 n^{3/5} + (\ell-1)
  \; \leq \; \frac{n x'_n}{2 \sigma}.
\]

\dkcomment{Unless I made a calculation mistake, we could replace a 12
  with a 10.}

Applying Lemma~\ref{lem:round-prob} to $\tau_{i,j}$,
we conclude that the probability that the error in coordinate $j$ of
arm $i$ exceeds $x'_s = g(s,\ell-1)$ at time $\tau_{i,j}$
(and hence at any time, by definition of $\tau_{i,j}$)
is at most
$24 \exp\left(-\frac{1.8 s x_s^2}{16 \sigma^2} \right)
\; = \; 24 \exp(-1.8 (\ell-1)^2)$.
Now, taking a union bound over all arms $i$ and
coordinates $j$ completes the proof.
\end{proof}

@@

\begin{proof}
The proof is similar to that of Lemma~\ref{lem:numP}.
Fix a sample path $\SP \in \Env{\ell}$.
Consider a phase $s > h(\ell)$ and a time $t$ in phase $s$.
Because $\SP \in \Env{\ell}$, in particular, all estimation errors are
bounded at time $t$, in the sense that the event \AccEU{t}{g(s,\ell)}
happens.
Because $s \geq h(\ell)$, we get that
$g(s,\ell) \leq \frac{\MinProb}{4 \Diam d \TieDensity}$
as well as $s \geq \exp(2/\MinProb)$.
Therefore, we can apply Lemma~\ref{lem:no-incentives} and conclude
that the pull at time $t$ was not incentivized.
\end{proof}
